A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
grammar

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session applies a single entropy reduction action,
whose execution can provide evidence regarding the truth value of an
active assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

>>>>

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session applies a single entropy reduction action,
whose execution can provide evidence regarding the truth value of a
{\em relevant} assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.
